\ttitle

### 2013-11-15 Chapters/Chapter5/artificial_data_generation.tex
Chapter 5 figures

First Takeuchi, reduced jumping mean:
$\epsilon_t$ is Gaussian with mean $0$ and variance $\sigma^2 = 1$, $a_1 = 0.6$ and $a_2 = -0.5$.

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance.eps}
  \caption[Jumping variance]{Jumping variance}
\end{figure}

>>>>

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_mean_takeuchi.eps}
  \caption[Jumping mean Takeuchi, set 1]{Jumping mean takeuchi, set 1}
  \label{fig:jumping_mean_takeuchi}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_mean_takeuchi_thresholds.eps}
  \caption[Jumping mean Takeuchi, set 1, thresholds]{Jumping mean takeuchi, set 1, thresholds}
\end{figure}

First Takeuchi, reduced jumping mean, Figure~\ref{fig:jumping_mean_takeuchi}:
$\epsilon_t$ is Gaussian with mean $0$ and variance $\sigma^2 = 1$, $a_1 = 0.6$ and $a_2 = -0.5$.

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance_mean_takeuchi.eps}
  \caption[Jumping variance and mean Takeuchi, set 2]{Jumping variance and mean takeuchi, set 2}
  \label{fig:jumping_variance_and_mean_takeuchi}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance_mean_takeuchi_thresholds_log_scale.eps}
  \caption[Jumping variance mean Takeuchi, set 2, thresholds]{Jumping variance and mean takeuchi, set 2, thresholds (log scale)}
\end{figure}

Second Takeuchi, jumping mean with $\Delta y = 1$ and $\sigma^2 = 0.1 / (0.01 + (10000 - x)/1000)$.
Figure~\ref{fig:jumping_variance_and_mean_takeuchi}.

@@

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/notes/jumping_variance.eps}
  \caption[Jumping variance]{Jumping variance, equal for Camci and Takeuchi, both set 3}
  \label{fig:jumping_variance_camci_takeuchi}
\end{figure}

Third Camci and Takeuchi, jumping variance.
When $y$ is odd, variance $\sigma^2$ changes from $1.0$ to $9.0$, and when $y$ is even variance $\sigma^2$ changes from $9.0$ to $1.0$.
See Figure~\ref{fig:jumping_variance_camci_takeuchi}.
